Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-06-29 snapshot_system/result.tex
revise
update graphs
Added two different versions of the extreme-binning efficiency comparison graph (still missing the CDS alg. efficiency). One is vertical and the other horizontal, not sure which is better.

\begin{figure}[htbp]
  \centering
  \epsfig{file=figures/parallel_backup.pdf, width=3.5in}
  \caption{Throughput per-node with concurrent snapshot backup tasks}
  \label{fig:parallel_backup}
\end{figure}

>>>>

\begin{figure}
    \centering
    \subfigure[Real VM backup performance]
    {
        \includegraphics[width=3in]{figures/parallel_backup_with_read.pdf}
        \label{fig:withread}
    }
    \\
    \subfigure[Deduplication and storage system performance]
    {
        \includegraphics[width=3in]{figures/parallel_backup_no_read.pdf}
        \label{fig:noread}
    }
    \caption{Throughput per-node with concurrent snapshot backup tasks}
    \label{fig:parallel_backup}
\end{figure}

% \begin{figure}[htbp]
%   \centering
%   \epsfig{file=figures/parallel_backup.pdf, width=3.5in}
%   \caption{Throughput per-node with concurrent snapshot backup tasks}
%   \label{fig:parallel_backup}
% \end{figure}

\subsection{Comparison with Other Approaches}
\subsubsection{Extreme Binning}
%\comments{
    %this version of the figure is vertical
    \begin{figure}[ht]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={Extreme-Binning Efficiency},
            ybar,
            bar width=1.00cm,
            symbolic x coords={Ex-Bin,CDS},
            xlabel={Algorithm},
            ylabel={Dedup. Efficiency (\%)},
            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
            xtick=data, %without this the symbolic coords may be repeated as filler
            enlarge x limits=0.6, %used to push plots towards center
            ymax=100,
            nodes near coords,
            nodes near coords align={vertical},
            ]
            \addplot coordinates {(Ex-Bin,90.16) (CDS,0)};
            \end{axis}
    \end{tikzpicture}
    \caption{Deduplication Efficiency
        ($efficiency=\frac{d-du}{d-du_{complete}}$)}
  \label{fig-exbin-efficiecy}
\end{figure}
%}
%same figure as above but horizontal (better for only two data points)
\begin{figure}[ht]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={Extreme-Binning Efficiency},
            xbar,
            width=7cm,
            height=3.5cm,
            %bar width=0.75cm,
            symbolic y coords={Ex-Bin,CDS},
            xlabel={Dedup. Efficiency (\%)},
            %ylabel={Algorithm},
            %extra x ticks={4.5,5.5,6.5} %to add extra ticks
            ytick=data, %without this the symbolic coords may be repeated as filler
            enlarge y limits=0.5,
            xmax=115, %otherwise label overlaps with right border
            nodes near coords,
            nodes near coords align={horizontal},
            ]
            \addplot coordinates {(90.16,Ex-Bin) (0,CDS)};
            \end{axis}
    \end{tikzpicture}
    \caption{Deduplication Efficiency
        ($efficiency=\frac{d-du}{d-du_{complete}}$)}
  \label{fig-exbin-efficiecy}
\end{figure}

\comments{
